---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `terrain`: Utility Functions for Terrain Derivatives Calculations 

<!-- badges: start -->
<!-- badges: end -->

The goal of `terrain` is to have a useful toolbox to calculate terrain derivatives using RSAGA. The package is for my personal use, with selected RSAGA terrain derivatives, and not meant to be comprehensive. Several defaults are hard-coded. 

For the package to work, there should be a local executable of the SAGA software available.

It is not meant for CRAN, and hence most of the functions will write to disk. 

## Installation

You can install the package from GitHub with:

```{r, eval = F}
remotes::install_github("loreabad6/terrain")
```


## RSAGA selected terrain derivatives

A list of the selected RSAGA terrain derivatives follows below, refer to function code documentation for a short description of each derivative. 

```{r, include = F}
library(dplyr)
library(kableExtra)
list = read.csv(
  'https://raw.githubusercontent.com/loreabad6/Earthflows_R/master/code_list.csv',
  sep = ';'
) %>% mutate(
  "Function" = case_when(
    Module == "ta_morphometry" ~ "`elev_to_morphometry()`",
    Module == "ta_lighting" ~ "`elev_to_lighting()`",
    Module == "ta_channels" ~ "`elev_to_channels()`",
    nchar(Code) > 2 ~ "`elev_to_terrain_analysis()`",
    Module == "ta_hydrology" ~ "`elev_to_hydrology()`"
  )
) %>% select(
    Derivative = Derivative_Name, 
    `Output Name` = File_Coding_Name, 
    Function) %>% 
  arrange(Function)
```

```{r, echo = F}
knitr::kable(list[, 1:2], escape = F) %>% 
  pack_rows(index = setNames(rle(list$Function)[[1]], rle(list$Function)[[2]]))
```
